The Eclipse Integrated Computational Environment

### 2019-07-31 src/content.tex
Fixed references.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

In previous work, Billings et al. interviewed modeling and simulation subject
matter experts to compile a list of requirements for implementing and using
these kinds of applications. In the process, they discovered that many of the
difficulties inherent in using high-performance modeling and simulation
software fall into five distinct categories \cite{billings_designing_2009}.
These activities, detailed in Section \ref{workflow-model}, include (1)
creating input, (2) executing jobs, (3) analyzing results, (4) managing data,
and (5) modifying code. There are many tools that address these problems
individually, but the same research found that the excess number and
specialization of these tools also contribute to the learning curve.

@@

Outside of the development team, ICE is commonly deployed as a sophisticated
user environment for computational science projects (see Section \ref{impact})
and as a visualization tool. The ICE source code originally contained a
significant amount of visualization support, but at the request of users in the
community, that support was ``spun off'' in early 2016 as the Eclipse Advanced
Visualization Project (EAVP)~\cite{billings_eclipse_2015}.

>>>>

In previous work, Billings et al. interviewed modeling and simulation subject
matter experts to compile a list of requirements for implementing and using
these kinds of applications. In the process, they discovered that many of the
difficulties inherent in using high-performance modeling and simulation
software fall into five distinct categories \cite{billings_designing_2009}.
These activities, detailed in Section \ref{workflow-model}, include (i)
creating input, (ii) executing jobs, (iii) analyzing results, (iv) managing
data, and (v) modifying code. There are many tools that address these problems
individually, but the same research found that the excess number and
specialization of these tools also contribute to the learning curve.

@@

Outside of the development team, ICE is commonly deployed as a sophisticated
user environment for computational science projects (see Section \ref{impact})
and as a visualization tool. The ICE source code originally contained a
significant amount of visualization support, but at the request of users in the
community, that support was ``spun off'' in early 2016 as the Eclipse Advanced
Visualization Project (EAVP) \cite{billings_eclipse_2015}.
